---
title: "V2 Status History Report"
author: "Dan Neilsen"
date: "September 13, 2016"
output:
  html_document:
    toc: true
    theme: united
---

<style type="text/css">
.main-container {
  max-width: 80%;
  margin-left: auto;
  margin-right: auto;
}

@media (min-width:320px) { /* smartphones, portrait iPhone, portrait 480x320 phones (Android) */ }
@media (min-width:480px) { /* smartphones, Android phones, landscape iPhone */ }
@media (min-width:600px) { /* portrait tablets, portrait iPad, e-readers (Nook/Kindle), landscape 800x480 phones (Android) */ }
@media (min-width:801px) { /* tablet, landscape iPad, lo-res laptops ands desktops */ }
@media (min-width:1025px) { /* big landscape tablets, laptops, and desktops */ }
@media (min-width:1281px) { /* hi-res laptops and desktops */ }
    
code {
  color: inherit;
  background-color: rgba(0, 0, 0, 0.04);
}
img {
  max-width:50%;
  height: auto;
}
.tabbed-pane {
  padding-top: 12px;
}
button.code-folding-btn:focus {
  outline: none;
}

h1 {
  font-size: 34px;
}
h1.title {
  font-size: 38px;
}
h2 {
  font-size: 38px;
}
h3 {
  font-size: 24px;
  font-weight: bold;
  border-bottom:1px solid #CCC;
}
h4 {
  font-size: 18px;
  font-weight: bold;
  color:2F5642;
}
h5 {
  font-size: 16px;
}
h6 {
  font-size: 12px;
}
.table th:not([align]) {
  text-align: left;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/RScripts")

library(dplyr)
library(ggplot2)
library(reshape2)
library(readxl)
library(plotly)
library(DT)
library(dygraphs)
library(data.table)
library(RColorBrewer)
library(knitr)
library(lattice)
library(lubridate)

fulldata <- read_excel("TMS - Load Tender Details_Current.xlsx")

colnames(fulldata)[2] <- "Responsible"

PlantOrder <- factor(c("GENEVA","RICHBURG","DEWITT","KINGSBURG","CORSICANA","CARLETON","OVERALL"))
factor(PlantOrder, levels = c("GENEVA","RICHBURG","DEWITT","KINGSBURG","CORSICANA","CARLETON","OVERALL"))
factor(PlantOrder, labels = c("GENEVA","RICHBURG","DEWITT","KINGSBURG","CORSICANA","CARLETON","OVERALL"))

MonthNamevalue <- factor(c(
"January","February","March","April","May","June","July","August","September","October","November","December"))
factor(MonthNamevalue, levels = c(
"January","February","March","April","May","June","July","August","September","October","November","December"))
factor(MonthNamevalue, labels = c(
"January","February","March","April","May","June","July","August","September","October","November","December"))

 fulldata$Month.Def <- months(as.Date(fulldata$Created.Date.and.Time))
 fulldata$Month.Rel <- months(as.Date(fulldata$Tender.Date.and.Time))
 fulldata$Month.Org <- months(as.Date(fulldata$Response.Date))
 fulldata$Month.Pick.Up.From <- months(as.Date(fulldata$Scheduled.Pick.Up.From))
 fulldata$Month.Pick.Up.To <- months(as.Date(fulldata$Scheduled.Pickup.To.Date))

```

## Report Definitions

This is a summary for the status window times based on V2 Statuses.

DEF: Created shipment and load

REL: Released for load planning and Tendered to carrier

ORG: Tender Accepted by carrier

START FROM: Planned loading start time

START TO: Required departure time to meet legal transit

Please make note that numbers reflect window timing between V2 statuses.

### Findings

####Richburg Summary
Richburg carriers have a faster response time for both tender acceptance and tender rejection.In viewing the DEF and REL statuses, Richburg has, on average, smaller DEF/creation to START TO/departure windows. Those smaller windows are exacerbated by a lowest monthly average(4 months) of 19.66 hours for a V2 status switch from DEF to REL.

Smaller timing windows, while they encourage faster acceptance/rejection, could potentially require more communication to keep shipments planned/organized. Currently, Richburg has highest number of filed plant related emails in Guardian.Loadmngt@penske.com since 08/22/2016(3 weeks of emails). The count is at 705 total emails with 57 unique chains referencing late or hot loads.

####Geneva Summary
Geneva has larger DEF to START TO windows, leading to scheduling loads much farther out, beneficial for special equipment lanes.

####Corsicana, Dewitt and Kingsburg Summary
On average, timing data is not extensive. 

### DEF V2 Status Summary

#### DEF to REL Status History 
(April through August)

```{r DeftoRel, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
DeftoRelbyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise(Mean.DEF.to.REL=mean(DEF.to.REL)) %>%
	mutate(Hours.DEF.to.REL=(Mean.DEF.to.REL/60))
	
DeftoRelbyplantweek$Month.Def <- factor(DeftoRelbyplantweek$Month.Def,levels=MonthNamevalue)

myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(DeftoRelbyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

DeftoRelplot <- ggplot(DeftoRelbyplantweek,aes(Month.Def,Hours.DEF.to.REL,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,100) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(DeftoRelplot)
cat("</td>")
cat("<td>")
DeftoRelTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(DEF.to.REL)/60),
			  "Min Hours"=(min(DEF.to.REL)/60),
			  "Max Hours"=(max(DEF.to.REL)/60)
			  )

DeftoRelbyplantweek$Month.Def <- factor(DeftoRelbyplantweek$Month.Def,levels=MonthNamevalue)
			  
datatable(DeftoRelTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

#### DEF to Start From Status History 
(April through August 2016)

```{r DeftoStartFrom, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
DeftoStartFrombyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise(DEF.to.START.FROM=mean(DEF.to.START.FROM)) %>%
	mutate(Hours=(DEF.to.START.FROM/60))

DeftoStartFrombyplantweek$Month.Def <- factor(DeftoStartFrombyplantweek$Month.Def,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(DeftoStartFrombyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

DeftoStartFrombyplantweek <- ggplot(DeftoStartFrombyplantweek,aes(Month.Def,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(DeftoStartFrombyplantweek)
cat("</td>")
cat("<td>")
DeftoStartFromTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(DEF.to.START.FROM)/60),
			  "Min Hours"=(min(DEF.to.START.FROM)/60),
			  "Max Hours"=(max(DEF.to.START.FROM)/60)
			  )
			  
datatable(DeftoStartFromTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

#### DEF to Start To Status History 
(April through August 2016)

```{r DeftoStartTo, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
DeftoStartTobyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise(DEF.to.START.TO=mean(DEF.to.START.TO)) %>%
	mutate(Hours=(DEF.to.START.TO/60))

DeftoStartTobyplantweek$Month.Def <- factor(DeftoStartTobyplantweek$Month.Def,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(DeftoStartTobyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

DeftoStartTobyplantweek <- ggplot(DeftoStartTobyplantweek,aes(Month.Def,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(DeftoStartTobyplantweek)
cat("</td>")
cat("<td>")
DeftoStartToTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Def>15 & Week.Num.Def<36) %>%
    group_by(Responsible,Month.Def) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(DEF.to.START.TO)/60),
			  "Min Hours"=(min(DEF.to.START.TO)/60),
			  "Max Hours"=(max(DEF.to.START.TO)/60)
			  )
			  
datatable(DeftoStartToTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

### REL V2 Status Summary

#### REL to ORG Status History 
(April through August 2016)

REL to ORG is based on tender offer time to tender accept time by the carrier. 

```{r RELtoORG, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
RELtoORGbyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise(REL.to.ORG=mean(REL.to.ORG)) %>%
	mutate(Hours=(REL.to.ORG/60))

RELtoORGbyplantweek$Month.Rel <- factor(RELtoORGbyplantweek$Month.Rel,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(RELtoORGbyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

RELtoORGbyplantweek <- ggplot(RELtoORGbyplantweek,aes(Month.Rel,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,15) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(RELtoORGbyplantweek)
cat("</td>")
cat("<td>")
RELtoORGTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(REL.to.ORG)/60),
			  "Min Hours"=(min(REL.to.ORG)/60),
			  "Max Hours"=(max(REL.to.ORG)/60)
			  )
			  
datatable(RELtoORGTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

#### REL to REJECTED Status History 
(April through August 2016)

REL to ORG-REJECTED is based on tender offer time to tender reject time by the carrier.

```{r RELtoRejected, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
RELtoORGbyplantweek <- fulldata %>%
    filter(Tender.Response=="Rejected" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise(REL.to.ORG=mean(REL.to.ORG)) %>%
	mutate(Hours=(REL.to.ORG/60))
	
RELtoORGbyplantweek$Month.Rel <- factor(RELtoORGbyplantweek$Month.Rel,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(RELtoORGbyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

RELtoORGbyplantweek <- ggplot(RELtoORGbyplantweek,aes(Month.Rel,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(RELtoORGbyplantweek)
cat("</td>")
cat("<td>")
RELtoORGTable <- fulldata %>%
    filter(Tender.Response=="Rejected" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(REL.to.ORG)/60),
			  "Min Hours"=(min(REL.to.ORG)/60),
			  "Max Hours"=(max(REL.to.ORG)/60)
			  )
			  
datatable(RELtoORGTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

#### REL to START FROM Status History 
(April through August 2016)

```{r RELtoStartFrom, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
RELtoStartFrombyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise(REL.to.START.FROM=mean(REL.to.START.FROM)) %>%
	mutate(Hours=(REL.to.START.FROM/60))

RELtoStartFrombyplantweek$Month.Rel <- factor(RELtoStartFrombyplantweek$Month.Rel,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(RELtoStartFrombyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

RELtoStartFrombyplantweek <- ggplot(RELtoStartFrombyplantweek,aes(Month.Rel,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(RELtoStartFrombyplantweek)
cat("</td>")
cat("<td>")
RELtoStartFromTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(REL.to.START.FROM)/60),
			  "Min Hours"=(min(REL.to.START.FROM)/60),
			  "Max Hours"=(max(REL.to.START.FROM)/60)
			  )
			  
datatable(RELtoStartFromTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

#### REL to START TO Status History 
(April through August 2016)

```{r ReltoStartTo, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
ReltoStartTobyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise(REL.to.START.TO=mean(REL.to.START.TO)) %>%
	mutate(Hours=(REL.to.START.TO/60))

ReltoStartTobyplantweek$Month.Rel <- factor(ReltoStartTobyplantweek$Month.Rel,levels=MonthNamevalue)
	
myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(ReltoStartTobyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

ReltoStartTobyplantweek <- ggplot(ReltoStartTobyplantweek,aes(Month.Rel,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(ReltoStartTobyplantweek)
cat("</td>")
cat("<td>")
ReltoStartToTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Rel>15 & Week.Num.Rel<36) %>%
    group_by(Responsible,Month.Rel) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(REL.to.START.TO)/60),
			  "Min Hours"=(min(REL.to.START.TO)/60),
			  "Max Hours"=(max(REL.to.START.TO)/60)
			  )
			  
datatable(ReltoStartToTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

### ORG V2 Status Summary

#### ORG to START TO Status History 
(April through August 2016)

Richburg data suggests the facility has the lowest average(excluding Corsicana) window of about 3 1/2 days lead time to shipment departure from tender acceptance.

```{r ORGtoStartTo, echo=FALSE,message=FALSE, results='asis',warning=FALSE, out.extra=''}
cat("<table class='container'><tr>")
cat("<td>")
ORGtoStartTobyplantweek <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Org>15 & Week.Num.Org<36) %>%
    group_by(Responsible,Month.Org) %>%
    summarise(ORG.to.START.TO=mean(ORG.to.START.TO)) %>%
	mutate(Hours=(ORG.to.START.TO/60))

myColors <- brewer.pal(5,"Set1")
names(myColors) <- levels(ORGtoStartTobyplantweek$Responsible)
colScale <- scale_colour_manual(name = "Responsible",values = myColors)

ORGtoStartTobyplantweek$Month.Org <- factor(ORGtoStartTobyplantweek$Month.Org,levels=MonthNamevalue)

ORGtoStartTobyplantweek <- ggplot(ORGtoStartTobyplantweek,aes(Month.Org,Hours,group = Responsible)) +
  geom_point(stat='summary', fun.y=sum,aes(color=Responsible)) +
  stat_summary(fun.y=sum, geom="line",aes(color=Responsible)) +
	colScale +
  ylim(0,500) +
    labs(x="Week Number",y="Number of Hours") +
  theme_bw() + theme( strip.background  = element_blank(),
                        panel.grid.major = element_line(colour = "grey80"),
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5))
	
ggplotly(ORGtoStartTobyplantweek)
cat("</td>")
cat("<td>")
ORGtoStartToTable <- fulldata %>%
    filter(Tender.Response=="Accepted" & Week.Num.Org>15 & Week.Num.Org<36) %>%
    group_by(Responsible,Month.Org) %>%
    summarise('# of Transactions' = n(),
              "Average Hours"=(mean(ORG.to.START.TO)/60),
			  "Min Hours"=(min(ORG.to.START.TO)/60),
			  "Max Hours"=(max(ORG.to.START.TO)/60)
			  )
			  
datatable(ORGtoStartToTable,rownames = FALSE, filter = 'none',colnames = c('Plant' = 1,'Month' = 2, '# of Loads' = 3)) %>%
  formatRound(c("Average Hours","Min Hours","Max Hours"), 2)
cat("</td>")
cat("</tr></table>")
```

